Point estimates comparison for the simplified Naomi model

### 2023-07-20 src/naomi-simple_point-estimates/point-estimates.Rmd
combine_two_plots() and combine_three_plots() for point estimate latent and output plots #55

sd_plot_latent_alt <- sd_plot_latent +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

y_axis <- ggplot(data.frame(l = mean_plot_latent$labels$y, x = 1, y = 1)) +
  geom_text(aes(x, y, label = l), angle = 90) +
  theme_void() +
  coord_cartesian(clip = "off")

mean_plot_latent_alt <- mean_plot_latent
mean_plot_latent_alt$labels$x <- ""
mean_plot_latent_alt$labels$y <- sd_plot_latent_alt$labels$y <- ""

(mean_sd_plot_latent_alt <- y_axis + (mean_plot_latent_alt / sd_plot_latent_alt) +
  plot_layout(widths = c(1, 30)))

ggsave("mean-sd-alt-latent.png", mean_sd_plot_latent_alt, h = 6, w = 6.25)
```

@@

@@

sd_plot_output_alt <- sd_plot_output +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "bottom"
  )

y_axis <- ggplot(data.frame(l = mean_plot_output$labels$y, x = 1, y = 1)) +
  geom_text(aes(x, y, label = l), angle = 90) +
  theme_void() +
  coord_cartesian(clip = "off")

mean_plot_output_alt <- mean_plot_output +
  theme(legend.position = "none")

mean_plot_output_alt$labels$x <- ""
mean_plot_output_alt$labels$y <- sd_plot_output_alt$labels$y <- ""

(mean_sd_plot_output_alt <- y_axis + (mean_plot_output_alt / sd_plot_output_alt) +
  plot_layout(widths = c(1, 30)))

ggsave("mean-sd-alt-output.png", mean_sd_plot_output_alt, h = 6, w = 6.25, bg = "white")
```

@@

plot_outputs(.indicator = "Posterior mean estimate", .par = "rho_t1_out", col = "#E69F00")
plot_outputs(.indicator = "Posterior mean estimate", .par = "lambda_t1_out", col = "#009E73")
plot_outputs(.indicator = "Posterior mean estimate", .par = "alpha_t1_out", col = "#56B4E9")
plot_outputs(.indicator = "Posterior SD estimate", .par = "rho_t1_out", col = "#E69F00")
plot_outputs(.indicator = "Posterior SD estimate", .par = "lambda_t1_out", col = "#009E73")
plot_outputs(.indicator = "Posterior SD estimate", .par = "alpha_t1_out", col = "#56B4E9")
```

>>>>

combine_two_plots <- function(plot1, plot2) {
  plot1alt <- plot1 +
    theme(legend.position = "none")

  plot2alt <- plot2 +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "none"
  )

  y_axis <- ggplot(data.frame(l = plot1$labels$y, x = 1, y = 1)) +
    geom_text(aes(x, y, label = l), angle = 90) +
    theme_void() +
    coord_cartesian(clip = "off")

  plot1alt$labels$x <- ""
  plot1alt$labels$y <- plot2alt$labels$y <- ""

  y_axis + (plot1alt / plot2alt) +
    plot_layout(widths = c(1, 35))
}

combine_two_plots(mean_plot_latent, sd_plot_latent)

ggsave("mean-sd-alt-latent.png", h = 6, w = 6.25)
```

@@

df_plot_output <- df_plot_output %>%
  mutate(par = fct_recode(par, "HIV prevalence" = "rho_t1_out", "ART coverage" = "alpha_t1_out", "HIV incidence" = "lambda_t1_out"))

@@

combine_two_plots(mean_plot_output, sd_plot_output)

ggsave("mean-sd-alt-output.png", h = 6, w = 6.25)
```

@@

mean_prev_plot <- plot_outputs(.indicator = "Posterior mean estimate", .par = "HIV prevalence", col = "#E69F00")
mean_inc_plot <- plot_outputs(.indicator = "Posterior mean estimate", .par = "HIV incidence", col = "#009E73")
mean_art_plot <- plot_outputs(.indicator = "Posterior mean estimate", .par = "ART coverage", col = "#56B4E9")
sd_prev_plot <- plot_outputs(.indicator = "Posterior SD estimate", .par = "HIV prevalence", col = "#E69F00")
sd_inc_plot <- plot_outputs(.indicator = "Posterior SD estimate", .par = "HIV incidence", col = "#009E73")
sd_art_plot <- plot_outputs(.indicator = "Posterior SD estimate", .par = "ART coverage", col = "#56B4E9")

#' Put together
combine_three_plots <- function(plot1, plot2, plot3) {
  plot1alt <- plot1 +
    theme(legend.position = "none")

  plot2alt <- plot2 +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "none"
  )

  plot3alt <- plot3 +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "none"
  )

  y_axis <- ggplot(data.frame(l = plot1$labels$y, x = 1, y = 1)) +
    geom_text(aes(x, y, label = l), angle = 90) +
    theme_void() +
    coord_cartesian(clip = "off")

  plot1alt$labels$x <- plot2alt$labels$x <- ""
  plot1alt$labels$y <- plot2alt$labels$y <- plot3alt$labels$y <- ""

  three_plots <- cowplot::plot_grid(plot1alt, plot2alt, plot3alt, ncol = 1)
  cowplot::plot_grid(y_axis, three_plots, ncol = 2, rel_widths = c(1, 35))
}

combine_three_plots(mean_prev_plot, mean_inc_plot, mean_art_plot)
ggsave("mean-alt-output.png", h = 7, w = 6.25)

combine_three_plots(sd_prev_plot, sd_inc_plot, sd_art_plot)
ggsave("sd-alt-output.png", h = 7, w = 6.25)
```
